---
title       : Iris Clasification
subtitle    : Data Reproducible Assesment
author      : Leticia Rodriguez Brey
job         : Data Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}

---

## Iris Classification application

This app helps you to predict the classification of an Iris specie. For the classification, the iris data set is used. You can find the data on this [link](https://archive.ics.uci.edu/ml/datasets/Iris)

The app predicts the specie from a given width and length measures of sepals and petals. Random Forest is used in order to predict the classification.



---

## Iris Data

This is a parallel plot. It helps us to identify paterns for each Iris specie and possible outliers.
```{r echo=FALSE}
# Create data directory
if(!file.exists("./data")){dir.create("./data")}
# Download the data file
url<-("http://archive.ics.uci.edu/ml/machine-learning-databases/iris/iris.data")
download.file(url, "./data/iris.csv",method="auto")
# Change to data directory for reading the data
setwd("./data/")
# Load datasets
iris <- read.csv("iris.csv", header=FALSE, sep=",")
#Nombre de las variables
colnames(iris)<-c("Sepal.Length","Sepal.Width","Petal.Length","Petal.Width","Species")
#Valor de cada variable para cada individuo, distinguiendo por especies, gráficos separados
library(lattice)
parallelplot(~iris[1:4]|Species,data=iris)
```

---

## Decision Tree and Random Forest

This is the classification table for the testing subset of the data. 
```{r echo=FALSE}
#DECISION TREE AND RANDOM FOREST
#Divide the data into training and testing (70%/30%)
set.seed(1234)
ind<-sample(2,nrow(iris),replace=TRUE,prob=c(0.7,0.3))
trainData<-iris[ind==1,]
testData<-iris[ind==2,]
#Build the decision tree
#load package party
library(party)
myFormula<-Species~Sepal.Length+Sepal.Width+Petal.Length+Petal.Width
iris_ctree<-ctree(myFormula,data=trainData)
testPred<-predict(iris_ctree,newdata=testData)
table(testPred,testData$Species)
```

---

## Iris classification APP

You can find and try out the application in the following [link](https://letirodribrey.shinyapps.io/Assessment/)

The application Github repository can be found on this [link](https://github.com/letirodribrey/ShinyApp)

The slidify Github repository is available in this [link](https://github.com/letirodribrey/Slidify)